Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-22 Paper/Manuscript.tex
Revert to alphabetical order for authors
Convert some hard-coded references to \citep's

To tap the full potential of broadband echosounder data, further methods for processing such data must be developed (Lavery et al., 2017; Basset et al., 2018). Examples include adapting pulses to improve target separation as well as further parameters from the individual targets. Different send pulses can be envisioned as well as various methods for acoustic target classification. The objective of this paper is to present a systematic and comprehensive explanation of how to process calibrated broadband echosounder data. By making associated code available, we provide a starting point for further developing signal processing methods for applying broadband acoustic to aquatic ecology.

@@

\section{Discussion}
The use of broadband signals in fisheries acoustics is a developing area and we anticipate many valuable enhancements will occur in the coming years. For example, the use of $\ts(\freqsym)$ and $\sv(\freqsym)$ to improve acoustic target classification \citep{bassettBroadbandEchosounderMeasurements2018, korneliussen2018}, and the potential of the high range resolution from pulse compression to observe small-scale fish behviours \citep{skaret2020} and to detect objects adjacent to boundaries \citep{lavery2017}. The basic formulation for calculating $\ts(\freqsym)$ and $\sv(\freqsym)$ presented here provides the foundation for future enhancements.

>>>>

To tap the full potential of broadband echosounder data, further methods for processing such data must be developed \citep{lavery2017,bassett_broadband_2018}. Examples include adapting pulses to improve target separation as well as further parameters from the individual targets. Different send pulses can be envisioned as well as various methods for acoustic target classification. The objective of this paper is to present a systematic and comprehensive explanation of how to process calibrated broadband echosounder data. By making associated code available, we provide a starting point for further developing signal processing methods for applying broadband acoustic to aquatic ecology.

@@

\section{Discussion}
The use of broadband signals in fisheries acoustics is a developing area and we anticipate many valuable enhancements will occur in the coming years. For example, the use of $\ts(\freqsym)$ and $\sv(\freqsym)$ to improve acoustic target classification \citep{bassett_broadband_2018, korneliussen2018}, and the potential of the high range resolution from pulse compression to observe small-scale fish behviours \citep{skaret2020} and to detect objects adjacent to boundaries \citep{lavery2017}. The basic formulation for calculating $\ts(\freqsym)$ and $\sv(\freqsym)$ presented here provides the foundation for future enhancements.
